### 2014-11-13 tex/intro.tex
reworked

In order to represent multiple heaps simultaneously in the context of
symbolic execution we define a novel heap representation and an
algorithm to initialize and update the heap on-the-fly. Our summary
heap approach supports aliasing, it does not require constraint
rewriting on heap updates, and it reduces the non-determinism in the
search space during symbolic execution.

\begin{comment}

The solution presented in this paper to enabling value sets in
symbolic execution with lazy initialization is to represent the heap
as a bipartite graph consisting of references and locations. A
reference is able to point to several different locations: each edge
predicated on constraints over aliasing between references. Locations
point back to references on different fields. The bipartite graph
enables (i) the use of aliasing to define objects rather than
recursive definitions; (ii) value set computation using only local
information; and (iii) heap updates that only impact affected
locations, require no constraint rewriting, and require no auxiliary
variables in the constraints.  We call this new heap a summary heap.

To mitigate state space explosion in GSE, the solution described in
paper uses a summary heap in the symbolic execution. This summary heap
algorithm defines how the bipartite graph updates in lazy
initialization. Unlike GSE, however, the summary heap algorithm
partitions only at points of divergence in the control flow
graph. These points of non-determinism are at field accesses or writes
that lead to null-pointer exceptions and at comparisons of
references. The former represents a divergence due to exceptional
control flow while the later due to program structure.

%In this work, we present a novel heap initialization and analysis
%technique which takes inspiration from both GSE and existing heap
%summarization techniques. The intuition behind our analysis is to
%construct the heap lazily during symbolic execution but reduce the
%points of non-determinism in the symbolic execution tree by analyzing
%each control-flow path only once for any given set of isomorphic
%heaps. To represent the exact set of feasible concrete heap
%structures resulting from execution of the control-flow path, we use
%a heap summary.

\end{comment}
We represent the heap as a bipartite graph consisting of references and locations. Each reference is able to point to multiple locations, where each edge is predicated on constraints over aliasing between references. Each location points to a single reference for a given field. The use of a bipartiate graph affords two
key advantages: (i) it allows for a non-recursive definition of objects which enables us to support aliasing, and (ii) it does not require rewriting of the constraints during updates to the heap nor does it introduce auxillary variables into the constraints.

>>>>

In this work, in order to effectively represent multiple heaps
simultaneously in the context of symbolic execution we define a novel
heap representation and an algorithm to initialize and update the heap
on-the-fly. Our summary heap approach supports aliasing, it does not
require constraint rewriting on heap updates, and it reduces the
non-determinism in the search space during symbolic execution.

We represent the heap as a bipartite graph consisting of references
and locations. Each reference is able to point to multiple locations,
where each edge is predicated on constraints over aliasing between
references. Each location points to a single reference for a given
field. The use of a bipartiate graph affords two key advantages: (i)
it allows for a non-recursive definition of objects which enables us
to support aliasing, and (ii) it does not require rewriting of the
constraints during updates to the heap nor does it introduce auxillary
variables into the constraints.
